Discovery of s-process stars in the LAMOST survey

### 2018-01-25 article/ms.tex
stuff on sodium enhancement

\subsection{Dynamics}
The dynamical analysis undertaken for our Barium star candidates was accomplished by crossing matching the sample with Gaia \citep{gaia2016a,gaia2016b} to produce 21 matches with proper motions, parallax, and galactic positions. We then, using the gala Python package, integrated our data to calculate the orbits of our 21 candidates with a Milky Way Potential model. The Milky Way potential implemented was constructed using a four component potential model built from a \citet{hernquist1990} bulge and nucleus, a \citet{miyamoto1975} disk, and the \citet{nfw1997} halo. In this potential, the disk and bulge parameters were adjusted to be consistent with previous work \citep{bovy2015}, and to vary the scale mass and radius, of the nucleus and halo, respectively. This potential model was used to integrate the orbits of our candidates back half a billion years, and compute distributions of orbital properties including orbital period, orbital energy, apocenter, eccentricity, and angular momentum in z. All stars are shown to have orbits consistent with being disk stars.

@@

\subsection{Sodium enhancment}
According to \citet{el1995}, sodium overabundance observed in the atmospheres of supergiants is synthesized by the NeNa reaction chain in the convective core of main-sequence stars. Sodium is transported to the surface of these supergiants via mixing of CNO cycle products during the first dredge-up, although, it is important to note sodium enhancement is not constrained to supergiant stars. Stars with a  minimum 1.5$M_\odot$ can exhibit sodium abundance similarily through the NeNa cycle \citep{denissenkov1987}. \citet{antipova2004} discovered a sodium enhancement in 16 of their Barium star candidates, they relate this to the dredge-up of nuclear-burning material produced by convection during the red-giant phase. Moreover, they suggest [Na/Fe] ratios exhibit systematically higher values for giants with lower log g values, but do not exhibit variations in metallicity. Similarily, \citet{decastro2016} highlights the possible weak, anti-correlation between [Na/Fe] ratio and log g, and illustrates this trend in previous studies\citep[e.g.][]{boyarchuk2002,mishenina2006,luck2007,takeda2008}.

It's important to highlight our research only discovered $<2$\,\% sodium presence in our 257 Barium candidates, contrary to previous studies \citep[e.g.][]{decastro2016}. This suggests systematic differences in the analyse undertaken by said previous studies. Also, synonymous to our s-process candidates, synthesized sodium is brought to the surface of giants via the first dredge-up, therefore, these candidates may display sodium enhancement without mass transfer from a TP-AGB star. And, in juxtaposition to the literature, our 5 sodium enhanced stars exhibit a surface gravity range between 2.98 and 3, showing no correlation between higher [Na/Fe] values and lower log g values. These considerations suggest sodium-rich material from the TP-AGB star polluted our 5 Barium candidates, but also, sodium enhancement is not unbiquitous in Barium Stars.

@@

\subsection{Extrinsic and intrinsic Barium stars}
Barium stars exist as either intrinsic or extrinsic objects. Intrinsic Barium stars must be massive enough to reach the TP-AGB phase, and extrinsic Barium stars must be in a binary with a previosuly polluting TP-AGB star companion. Figure \ref{fig:figure2} demonstrates the majority of our Barium star sample has a surface gravity greater then 2, highlighting that our sample is primarily not massive enough to have reach the TP-AGB phase and therefore, must be extrinsic Barium stars. Furthermore, this suggests other enhancements including our 5 sodium and 178 carbon enhanced Barium stars exist through TP-AGB companion pollution.

>>>>

\subsection{Dynamics}
We integrated galactic orbits for 21 Barium stars using recent astrometry from Gaia/TGAS \citep{gaia2016a,gaia2016b}. Using the \texttt{gala} Python package, we integrated each star backwards for $0.5\,\textrm{Gyr}$ in a Milky Way-like potential that consists of four components: a \citet{hernquist1990} bulge and nucleus, a \citet{miyamoto1975} disk, and the \citet{nfw1997} halo. In this potential, the disk and bulge parameters were adjusted to be consistent with previous work \citep{bovy2015}, and to vary the scale mass and radius, of the nucleus and halo, respectively. We computed orbital periods, energy, apocenters, pericenters, eccentricities, and angular momentum in the $z$-direction. All 21 stars showed prograde orbits that were consistent with membership in the Milky Way disk.

@@

\subsection{Extrinsic and intrinsic Barium stars}
Barium stars exist as either intrinsic or extrinsic objects. Intrinsic Barium stars must be massive enough to reach the TP-AGB phase, and extrinsic Barium stars must be in a binary with a previously polluting TP-AGB star companion. Figure \ref{fig:figure2} shows that the majority of our Barium stars have $\log{g} > 2$, highlighting that most stars in our sample are not massive enough to have already reached the TP-AGB phase and therefore, must be extrinsic Barium stars. The classification for Barium stars with $\log{g} < 2$ is uncertain: these stars could be intrinsic or extrinsic. From here on when we refer to extrinsic Barium stars, we specifically refer to those with $\log{g} > 2$.

\subsection{Sodium enhancment}
According to \citet{el1995}, sodium overabundances observed in the atmospheres of supergiants is synthesised by the NeNa reaction chain in the convective core of main-sequence stars. Sodium is transported to the surface of these supergiants via mixing of CNO cycle products during the first dredge-up, although, it is important to note sodium enhancement is not constrained to supergiant stars. Stars with a  minimum mass of $1.5\,M_\odot$ can also exhibit enhanced sodium abundances through the NeNa cycle \citep{denissenkov1987}. \citet{antipova2004} reported sodium enhancements in 16\todo{/??} of their Barium star candidates, and they relate this to the dredge-up of nuclear-burning material produced by convection during the red-giant phase. Moreover, they suggest [Na/Fe] ratios exhibit systematically higher values for giants with lower $\log{g}$ values, but do not exhibit variations in metallicity. Similarly, \citet{decastro2016} highlights the possible weak anti-correlation between [Na/Fe] ratio and $\log{g}$, and highlights that this trend in previous studies \citep[e.g.][]{boyarchuk2002,mishenina2006,luck2007,takeda2008}.

We find only $<2$\,\% of our Barium stars show sodium enhancement, contrary to previous studies \citep[e.g.][]{decastro2016}. We also note that the 5 sodium-enhanced Barium stars all have $\log{g} \approx 3$, not at lower $\log{g}$ values as might be expected if low $\log{g}$ values systematically contributed to higher [Na/Fe] abundance ratios. These results suggest that sodium-rich material from a companion TP-AGB star has polluted these 5 Barium candidates, but importantly, sodium enhancement is by no means ubiquitous in Barium stars. The comparisons made in \citep{decastro2016} made use of multiple literature comparisons, and therefore it is possible that there are systematic differences (biases) between Milky Way studies of normal FGK-type stars and those focussed on Barium stars, leading to unresolved differences in the reported [Na/Fe] abundance ratio. These same systematic effects could contribute to the observed correlation between [Na/Fe] and $\log{g}$, which we do not observe in our sample.

% Could be removed:
%Also, synonymous to our s-process candidates, synthesised sodium is brought to the surface of giants via the first dredge-up, therefore, these candidates may display sodium enhancement without mass transfer from a TP-AGB star.

%Furthermore, this suggests other enhancements including our 5 sodium and 178 carbon enhanced Barium stars exist through TP-AGB companion pollution.

@@
